Limited plasticity but increased variance in physiological rates across ectotherm populations under climate change

### 2025-01-03 ms.qmd
Finsihed dealing with figure comment for R1

```{r, fig-sim2}
#| label: fig-sim2
#| fig-align: center
#| fig-cap: "Results from sensitivity analysis. Expected $lnVR_{Q_{10}}$ from simulated performance curves when varying among-individual variance in thermal breadth ($\\sigma_{\\delta}$ = {0.01, 2}) and  thermal maxima ($\\sigma_{\\sigma}$ = {0.01, 2}) while fixing the rate variance constant ($\\sigma_{\\alpha}$ = 0.01). In all simulations, population parameters were $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{\\delta}$ and $\\sigma_{\\sigma}$. The parameter space that matches the observed mean $lnVR_{Q_{10}}$ for terrestrial (green), marine (orange) and freshwater (blue) ectotherms is highlighted. Dashed lines indicate the relative differences between the three habitat types when holding one variance parameter constant."

>>>>

```{r, fig-sim2}
#| label: fig-sim2
#| fig-align: center
#| fig-cap: "Performance curve simulations for the expected $lnVR_{Q_{10}}$ when varying among-individual variance in thermal breadth ($\\sigma_{\\delta}$ = {0.01, 2}) and  thermal maxima ($\\sigma_{\\sigma}$ = {0.01, 2}) while fixing the rate variance constant ($\\sigma_{\\alpha}$ = 0.01). In all simulations, population parameters were $\\delta$ = 35, $\\sigma$ = 9, $\\alpha$ = -15, and *n* = 1000 individuals were simulated for each combination of $\\sigma_{\\delta}$ and $\\sigma_{\\sigma}$. The parameter space that matches the observed mean $lnVR_{Q_{10}}$ from our meta-analysis for terrestrial (green), marine (orange) and freshwater (blue) ectotherms is labelled and highlighted. Dashed lines indicate the relative differences between the three habitat types when holding one variance parameter constant."
